---
title: "Weekly exercise 2"
output: 
  learnr::tutorial:
    theme: "sandstone"
    css: css/styles.css
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library("learnr")
knitr::opts_chunk$set(echo = TRUE)
```

## Question 7 a)

Use `ggplot()` to plot the following on a single plot for `x` axis values from `-5` to `5`.

i. Probability density curve of $N(0,1)$ using `dnorm()` in `black`
solid line.
ii. Probability density points of $N(0,1)$ evaluated multiples of `0.25`
with `blue` filled circles without using `dnorm()`.
iii. Probability density curve of $N(3,0.5^2)$ using `dnorm()` in `black`
dotted line.
iv. Probability density points of $N(3,0.5^2)$ evaluated multiples of `0.25`
with `red` empty circles without using `dnorm()`.

```{r plot, exercise=TRUE, exercise.lines=25}
library(ggplot2)
x <- seq(-5, 5, 0.01) # x values for creating plots
x25 <- # create a vector of valuse from -5 to t
d1 <- dnorm(x...) # 
d2 <- (1 / sqrt(2 * pi)) # complete the density function; pi is a prepopulated constant
d3 <- dnorm(x...) #
d4 <- (1 / 0.5 * sqrt(2 * pi)) # complete the density function; pi is a prepopulated constant

ggplot() + # complete the ggplot function
```


## Question 7 b)

Suppose Lena owns two coffee shops. At her first shop, the number of daily
customers, $R$, follows $\text{Pois}(50)$. At her second shop, the number of
daily customers, $S$, follows $\text{Pois}(30)$. Let $T=R+S$, the total daily
customers. Use R's built-in functions to randomly sample from Poisson distributions
to simulate 100,000 days and estimate the median of $T$ by computing the median
of the simulated $T$ values.

```{r sim-cards, exercise=TRUE, exercise.lines=25}
N <- 10^5 # 100,000 simulations
sims <- cbind(
  # sample from R,
  # sample from S
)
simT <- # store simulated totals
# compute the probability estimates
```

> `cbind(x, y)` combines vectors into a matrix as columns.

